---
title: "HomeWork_1_22208626"
author: "Jacques-Emmanuel"
date: today
date-format: long
format: html
theme: [default, custom.scss]
execute: 
  eval: true
  echo: false
editor: visual
---

# Presentation of the R airquality dataset

## Descriptive statistics of the Wind and Temp variables

```{r}
#| label: Loading airquality dataset

#Load dataset
data('airquality')

#Remove NA value from the data
airquality_no_na <- na.omit(airquality)

#summary of the temp and wind variables
summary(airquality_no_na[c(3,4)])

```

The median and mean of the Wind variable are almost equal so the wind variable has a **symmetric** distribution. Whereas, the Temp variable distribution is **left skewed** because the median is greater than the mean. This could be explained by the fact that we observe few high temperature during month 8 and month 9.

## Plot of the Wind varibale against the Temp variable

We are interested in the degree of correlation between the Wind and the temp variables.

```{r}
#| label: packages
#| echo: false
#| message: false

#loding ggplot2 and plotly libraries
library(ggplot2)
library(plotly)
```


```{r}
#| label: ggplot
#| echo: false
#| fig-width: 10
#| fig-height: 5

#Plot scatter plot of the Temp variable vs the Wind variable

p <- ggplot(airquality_no_na, aes(x = Temp, y = Wind, col = Month)) + 
  geom_point()
ggplotly(p)

```


Below are the observations on the plot:

- We observe a **strong negative** relationship between the the wind and the Temp variables. The Wind variable is decreasing as the Temp variable is increasing.

- The lowest temperature are observed during **month 5**. Whereas the highest temperature are observed during **month 8**.